In-silico molecular enrichment and clearance of the human intracranial space

### 2025-06-20 paper/main.tex
Add data availability statement.

>>>>

\section*{Data availability}

The software developed to generate and analyze the numerical results
of this study are openly available on Zenodo with the identifier doi:
10.5281/zenodo.14749163. In addition to simulation and analysis
software, this archive also includes surface triangulations used for
geometry representation, computational meshes (3D meshes and 1D
networks), segmentations, sample simulation outputs from the baseline
and high PVS flow models, and animations.
